---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shinyproxyLogs

<!-- badges: start -->
<!-- badges: end -->

shinyproxyLogs is an R package designed to simplify the process of parsing and analyzing log files generated by ShinyProxy containers. The package provides a set of functions that allow users to extract metadata from log filenames and compute summary statistics from log content. This helps system administrators and developers quickly identify issues such as errors, warnings, and fatal events in their ShinyProxy logs.

# Project Goal

The primary goal of shinyproxyLogs is to automate and streamline the log analysis process for ShinyProxy environments. Specifically, the package:

- **Parses Log File Names**: Extracts important metadata such as `specId`, `proxyId`, `startupTime`, and `logType` from the log file names.
- **Analyzes Log Content**: Reads the log files and computes statistics including the total number of lines, and counts of error, warning, and fatal messages.
- **Provides Summary Reports**: Aggregates data by container (based on the metadata) to offer a concise overview of the container logs.

# Prerequisites

**Access Rights:**
To use shinyproxyLogs, you must have the necessary access rights to the `shinyproxy` folder. This folder contains the logs from the ShinyProxy container, and without proper permissions, the package will not be able to read or process the log files. Please ensure that you have the required read and access permissions to the ShinyProxy logs directory before using this package.

## Installation

From CRAN

``` r
install.packages("shinyproxyLogs")
```

You can install the development version of shinyproxyLogs like so:


``` r
install.packages("devtools")
devtools::install_github("tsenegas/shinyproxyLogs")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(shinyproxyLogs)
## basic example code
analyze_logs(path_container_logs = '../../shinyproxy/shinyproxy/container-logs/logs/')
```

